COG-ED Manuscript

### 2022-01-10 06_Paper/COG-ED/Manuscript.Rmd
put full pilot results in supplementary

  # H1a: Performance measured by signal detection d’ declines with increasing n-back level.

@@

  # H1b: Performance measured by reaction time declines with increasing n-back level.

@@

  row.names(h2b_result.table) <- NULL
  h2b_result.table$Parameter[1:6] <- c("Intercept", "N-Back Level", "NFC", "d'", "RT", "Level x NFC")

@@

  table_1 <-
    kbl(h2b_result.table,
    caption = "Effects of n-back load level on subjective value controlled 
    for task performance (d’ and reaction time), correct and postcorrect trials.",
    booktabs = T,                          # no vertical lines
    escape = F,                            # correctly print special characters)
    align = c("l",rep("r",7))) %>%         # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    footnote(general = "NFC = Need for Cognition, SE = standard error. ***$p$ < .001, **$p$ < .01, *$p$ < 0.5.",
            escape = F,                    # correctly print special characters
            threeparttable = T)            # line breaks in the footnote

@@

>>>>

  # H1a: The signal detection measure d’ declines with increasing n-back level.

@@

  # H1b: Reaction time increases with increasing n-back level.

@@

  row.names(h2b_result.table) <- NULL
  h2b_result.table$Parameter[1:6] <- c("Intercept", "n-back level", "NFC", "d'", "RT", "level x NFC")

@@

  table_1 <-
    kbl(h2b_result.table,
    caption = "Effects of n-back load level on subjective value controlled 
    for task performance (d' and reaction time), correct and postcorrect trials.",
    booktabs = T,                          # no vertical lines
    escape = F,                            # correctly print special characters)
    align = c("l",rep("r",7))) %>%         # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    footnote(general = "NFC = Need for Cognition, SE = standard error. ***$p$ < .001, **$p$ < .01, *$p$ < 0.5.",
            escape = F,                    # correctly print special characters
            threeparttable = T)            # line breaks in the footnote

@@

### Hypothesis 1a: The signal detection measure d' declines with increasing n-back level.

ANOVA:

`r apa_print(hypothesis1a_rmanova)$full_result`

Paired contrasts:

`r hypothesis1a_contrasts`

### Hypothesis 1b: Reaction time increases with increasing n-back level.

ANOVA:

`r apa_print(hypothesis1b_rmanova)$full_result`

Paired contrasts:

`r hypothesis1b_contrasts`

### Hypothesis 1c: Ratings on all NASA-TLX dimensions increase with increasing n-back level.

Mental subscale ANOVA:

`r apa_print(hypothesis1c_mental_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_mental_BF)$bf`

Mental subscale paired contrasts:

`r hypothesis1c_mental_contrasts`

Physical subscale ANOVA:

`r apa_print(hypothesis1c_physical_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_physical_BF)$bf`

Physical subscale paired contrasts:

`r hypothesis1c_physical_contrasts`

Time subscale ANOVA:

`r apa_print(hypothesis1c_time_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_time_BF)$bf`

Time subscale paired contrasts:

`r hypothesis1c_time_contrasts`

Performance subscale ANOVA:

`r apa_print(hypothesis1c_performance_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_performance_BF)$bf`

Performance subscale paired contrasts:

`r hypothesis1c_performance_contrasts`

Effort subscale ANOVA:

`r apa_print(hypothesis1c_effort_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_effort_BF)$bf`

Effort subscale paired contrasts:

`r hypothesis1c_effort_contrasts`

Frustration subscale ANOVA:

`r apa_print(hypothesis1c_frustration_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_frustration_BF)$bf`

Frustration subscale paired contrasts:

`r hypothesis1c_frustration_contrasts`

### Hypothesis 2a: Subjective values decline with increasing n-back level.

ANOVA:

`r apa_print(hypothesis2a_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis2a_BF)$bf`

Paired contrasts:

`r hypothesis2a_contrasts`

### Hypothesis 2b: Subjective values decline with increasing n-back level, even after controlling for declining task performance measured by signal detection d’ and reaction time.

Multi level model:

`r table_1`

### Hypothesis 2c: Subjective values decline stronger with increasing task load for individuals with low compared to high NFC scores.

Simple slopes analysis:

`r h2b_ss.table`

Johnson-Neyman intervals:

`r h2b_jn.int`

### Hypothesis 3a: Subjective values positively predict individual NCS scores.

Intercept:
`r apa_print(hypothesis3a)$estimate$Intercept`

Predictor $AxAUC$:
`r apa_print(hypothesis3a)$estimate$h3_data_axauc`

Fit:
`r apa_print(hypothesis3a)$estimate$modelfit$r2`

$BF10=$ `r extractBF(hypothesis3a_BF)$bf`

### Hypothesis 3b: NASA-TLX scores negatively predict individual NFC scores.

Intercept:
`r apa_print(hypothesis3b)$estimate$Intercept`

Predictor $AxAUC$:
`r apa_print(hypothesis3b)$estimate$h3_data_axauc`

Predictor AUC NASA-TLX:
`r apa_print(hypothesis3b)$estimate$h3_data_auc_ntlx`

Fit:
`r apa_print(hypothesis3a)$estimate$modelfit$r2`

$BF10=$ `r extractBF(hypothesis3b_BF)$bf`
